Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Tutorial Using Cutting-Edge Tools

### 2021-01-12 paper_contents.tex
Tutorial instead of workshop
Add call for participation

\title{Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools}
\author{     }
\date{     }

@@

>>>>

\title{Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Tutorial Using Cutting-Edge Tools}
\author{     }
\date{     }

@@

Have you ever struggled with formatting your papers in accordance with ISLS conference proceedings guidelines? Do you want to seamlessly integrate a part of research analysis (e.g., computational results, figures, and tables) into your paper in a programmatic fashion? Or, would you like to produce your ISLS conference paper in multi-formatted and accessible outputs?

If you say “Yes” to any of these, this tutorial is for you. This half-day event focuses on computational word processing that brings you both reproducibility and accessibility. The three organizers of this tutorial have developed an easy-to-write authoring template tailored for the ISLS conference proceedings.

Based on LaTeX, a publication-quality typesetting system, we have made two options for the ISLS community use: (1) Collaborative writing on Overleaf website. (2) Literate programming using statistical-computing R + Markdown environment.

No background in either LaTeX or R Markdown is required. Participants will learn how to create an reproducible and accessible paper for the ISLS conference submission using the step-by-step computational word processing workflow that the three authors propose. The following includes the core activities that the tutorial will cover:

\begin{itemize}
  \item Getting started with LaTeX, Overleaf, and R Markdown.
  \item Inserting texts, figures, tables, and citations.
  \item Embedding statistical-computing results from R and/or Python.
  \item Rendering multi-formatted and accessible outputs.
  \item Compiling and debugging tips.
\end{itemize}

Participants will be asked to attend this session with some required software dependencies installed on their laptops and to bring either existing or work-in-progress paper content, all of which will be timely reminded via email beforehand.
